\section{Introduction}
    \subsection{Motivation}\label{Motivation}
    %Tell the reader about my plan
	In this paper we want to illustrate the impact of climate change through visual transformations using Generative Adversarial Networks (GANs). 
	%what is it all about
	Tackling the climate crisis is one of the most urgent issues in this century\footnote{https://www.un.org/en/sections/issues-depth/climate-change/}. Countermeasures are complex and demand the cooperation between nations, businesses and cultures. Hence, the more important it is that everyone pulls together\footnote{https://www.un.org/sustainabledevelopment/climate-change/}. Nevertheless, there are many people who are not aware of the dimensions of climate change or even deliberately deny them or, in the worst case, accelerate climate change. \\
	Admittedly, most people only notice those consequences directly that are not yet threatening, such as rising temperatures. Because of this, an average person cannot yet deduce the final intensity that might follow. The Optimism Bias\footnote{https://en.wikipedia.org/wiki/Optimism\_bias} is the key word here that makes many people think that everything changes again for the positive or that they are not affected.
	Even pictures of catastrophes such as floods or melting icebergs appear far away and not harmful. Some have the pictures in the back of their minds, but those vanish again during their everyday life. \\
	The lack of psychological affection\cite{behavioural} is the gap we want to close. In this report, we would like to focus on houses that were set on fire by a forest fire, a typical consequence of climate change.
	%how do I do it 
	We would like to take action against the presented misjudgments by showing the deniers which effects climate change can have on them, and in this case their house. This work is intended to be the cornerstone for a longer project. To be precise, we create a model that does not create real, but realistic looking images from a lot of pictures of burning houses as the first step.\\
    